The function-sheaf dictionary for smooth commutative group schemes over finite fields

### 2014-08-25 crelle-dictionary.tex
New abstract.

\begin{abstract}
Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
this paper extends Deligne's function-sheaf dictionary to smooth commutative group schemes over finite fields.
\end{abstract}

>>>>

\begin{abstract}
By extending the scope of function-sheaf dictionary for connected commutative algebraic groups, we find a geometrization of characters of all smooth commutative group schemes over finite fields.
As an application, we explain how to geometrize and categorify quasicharacters of all connected commutative algebraic groups over non-Archimedean local fields that admit a locally finite type Neron model, such as algebraic tori, abelian varieties and unipotent K-wound groups.
\end{abstract}
